AvoidFutRessimpletest

### 2021-12-16 R/AvoidFutRessimpletest.Rmd
Treefelling end!!

inventory <- suppressMessages(treeselection(inventory, objective = 20, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = TRUE, topography = DTMParacou, 
                                            plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
ind <- inventory %>%
  dplyr::filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
                CrownDiameter,Selected, Xutm, Yutm) %>% 
  sample_n(1) %>% 
  tibble::add_column(TreeFellingOrientationSuccess = "1")

ind$Xutm <- 286546.1
ind$Yutm <- 583029.1
Foot <- st_point(c(ind$Xutm,ind$Yutm))
```

@@

# at the same y than the tree to be felled
# 1 on the right side
FutureReserveCrowns[1,]$Xutm <- ind$Xutm + 30
FutureReserveCrowns[1,]$Yutm <- ind$Yutm + 10

# 1 on the left side
FutureReserveCrowns[2,]$Xutm <- ind$Xutm - 30 
FutureReserveCrowns[2,]$Yutm <- ind$Yutm + 10

@@

```{r}
# The crown
Crown <- ind %>%
  mutate(xCrown = Xutm,
         yCrown = Yutm + TrunkHeight + CrownHeight/2,
         exCrown = CrownDiameter/2,
         eyCrown = CrownHeight/2) %>%
  st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse

# The trunk
Trunk <- with(ind,
              st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm) # the return
                                     ,ncol=2, byrow=TRUE))))

@@

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

@@

  theta <- 360 - numeric(matlib::angle(c(Foot[1] - Foot[1], ind$TreeHeight),
                                       c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
}

## when the tree is on the trail (no angle)
if(is.na(theta)) theta <- 0
thetaIndNearest <- theta
rm(theta)
```

@@

# if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
if(any(FutureReserveCrowns$TreeHeight <= ind$TreeHeight)){

  FutResCrownsPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight <= ind$TreeHeight) %>% 
    mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
    summarise(Points = st_combine(Crowns)) # several multipoints to 1
}

# if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
if(any(FutureReserveCrowns$TreeHeight > ind$TreeHeight)){

  FutResDBHPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight > ind$TreeHeight) %>% 
    rowwise() %>% 
    mutate(Points = st_point(c(Xutm, Yutm)) %>% 
             st_buffer(dist = DBH/2) %>% 
             st_cast("MULTIPOINT") %>% 
             st_sfc()) %>% 
    ungroup() %>% 
    summarise(Points = st_combine(Points)) # several multipoints to 1
}

@@

```{r}
FootBuffer <- ind %>% 
  mutate(Points = st_point(c(Xutm, Yutm)) %>% 
           st_buffer(dist = CrownDiameter/2) %>% 
           st_cast("MULTIPOINT") %>% 
           st_sfc())
# Multipoints to points
FootBuffer <- st_cast(st_sfc(FootBuffer$Points), "POINT", group_or_split = TRUE)
```

@@

# Distances and angles
```{r}

# Only Foots 
# FutResAllPoints <- FutureReserveCrowns %>% 
#    select(Xutm, Yutm)
# 
# FutResFoots <- st_multipoint(x = as.matrix(FutResAllPoints)) # all the future/reserve trees foot
# FutResAllPoints <- st_cast(st_sfc(FutResFoots), "POINT", group_or_split = TRUE) # multiple points

# Distances between each of these points and Foot
RotationAngle <- c() # empty list for rotation angles
for (FRP in 1:length(FutResAllPoints)) { # for each point
  FutResDist <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point

  # If distances < TreeHeight of the tree to be felled
  if(FutResDist < ind$TreeHeight){
    # sum(FutResDists < ind$TreeHeight) # check av/res trees close to the tree to be felled

@@

        RotationAngle <- c(RotationAngle, as.numeric(matlib::angle(
          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], ind$TreeHeight), # default position
          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
          degree = TRUE)))

@@

        RotationAngle <- c(RotationAngle,  360 - as.numeric(matlib::angle(
          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], ind$TreeHeight), # default position
          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - 
              FootBuffer[[P]][2]), # position to avoid
          degree = TRUE)))
      }
    }
  }
}
rm(FutResDist)
      # sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed

    ## Then the angle to the trail: the angle to avoid
OppAngToAvoid <- RotationAngle - 180 - thetaIndNearest # valeurs négatives c'est là le prblm
TrailAnglesToAvoid <- 180-(90 + OppAngToAvoid)
TrailAnglesToAvoid <- round(TrailAnglesToAvoid, digits = 0)
TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] <- TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] - 360
AnglesToAvoid <- TrailAnglesToAvoid[
  TrailAnglesToAvoid >= 1 & TrailAnglesToAvoid <= 179
]
```

@@

```{r}
# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
if(ind$TreeFellingOrientationSuccess == "1"){

@@

    Aangle <- round(as.numeric(180 + OppAng + thetaIndNearest), digits = 0) # Foot oriented

@@

    Aangle <- round(as.numeric(360 - OppAng + thetaIndNearest), digits = 0) # Foot oriented
  }

@@

}else{ # else random felling
  RandomAngle <- as.numeric(sample(c(0:359.9), size = 1))

>>>>

inventory <- suppressMessages(treeselection(inventory, objective = 20, scenario ="manual",
                                            fuel = "2", diversification = TRUE, specieslax = FALSE,
                                            objectivelax = TRUE, topography = DTMParacou, 
                                            plotslope = PlotSlope,
                                            speciescriteria = SpeciesCriteria,
                                            advancedloggingparameters = loggingparameters())$inventory)
dat <- inventory %>%
  dplyr::filter(Selected == "1") %>%
  dplyr::select(idTree,DBH,TrunkHeight,TreeHeight,CrownHeight,
                CrownDiameter,Selected, Xutm, Yutm) %>% 
  sample_n(1) %>% 
  tibble::add_column(TreeFellingOrientationSuccess = "1")

dat$Xutm <- 286546.1
dat$Yutm <- 583029.1
Foot <- st_point(c(dat$Xutm,dat$Yutm))
```

@@

# at the same y than the tree to be felled
# 1 on the right side
FutureReserveCrowns[1,]$Xutm <- dat$Xutm + 30
FutureReserveCrowns[1,]$Yutm <- dat$Yutm + 10

# 1 on the left side
FutureReserveCrowns[2,]$Xutm <- dat$Xutm - 30 
FutureReserveCrowns[2,]$Yutm <- dat$Yutm + 10

@@

```{r}
# The crown
Crown <- dat %>%
  mutate(xCrown = Xutm,
         yCrown = Yutm + TrunkHeight + CrownHeight/2,
         exCrown = CrownDiameter/2,
         eyCrown = CrownHeight/2) %>%
  st_as_sf(coords = c("xCrown", "yCrown")) # ellipse centroid coordinates
Crown <- st_ellipse(Crown, Crown$exCrown, Crown$eyCrown) # create the ellipse

# The trunk
Trunk <- with(dat,
              st_polygon(list(matrix(c(Xutm-(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm + TrunkHeight,
                                       Xutm+(DBH/100)/2, Yutm,
                                       Xutm-(DBH/100)/2, Yutm) # the return
                                     ,ncol=2, byrow=TRUE))))

@@

  theta <- as.numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                    c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))

@@

  theta <- 180 - numeric(matlib::angle(c(Foot[1] - Foot[1], dat$TreeHeight),
                                       c(TrailPt[1] - Foot[1], TrailPt[2] - Foot[2]), degree = TRUE))
}

## when the tree is on the trail (no angle)
if(is.na(theta)) theta <- 0L
theta <- theta
```

@@

# if the fut/res tree is smaller or of the same height than the tree to be felled: we have to avoid the crown too
if(any(FutureReserveCrowns$TreeHeight <= dat$TreeHeight)){

  FutResCrownsPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight <= dat$TreeHeight) %>% 
    mutate(Crowns = st_cast(Crowns, "MULTIPOINT")) %>% # polygon to multipoint
    summarise(Points = st_combine(Crowns)) # several multipoints to 1
}

# if the fut/res tree is taller than the tree to be felled: we will only avoid it on its DBH
if(any(FutureReserveCrowns$TreeHeight > dat$TreeHeight)){

  FutResDBHPoints <- FutureReserveCrowns %>% 
    filter(TreeHeight > dat$TreeHeight) %>% 
    rowwise() %>% 
    mutate(Points = st_point(c(Xutm, Yutm)) %>% 
             st_buffer(dist = DBH/2) %>% 
             st_cast("MULTIPOINT") %>% 
             st_sfc()) %>% 
    ungroup() %>% 
    summarise(Points = st_combine(Points)) # several multipoints to 1
}

@@

```{r}
FootBuffer <- dat %>% 
  mutate(Points = st_point(c(Xutm, Yutm)) %>% 
           st_buffer(dist = CrownDiameter/2) %>% 
           st_cast("MULTIPOINT") %>% 
           st_sfc())
# Multipoints to points
FootBuffer <- st_cast(st_sfc(FootBuffer$Points), "POINT", group_or_split = TRUE)
```

@@

# Distances and angles
```{r}
# Only Foots 
# FutResAllPoints <- FutureReserveCrowns %>% 
#    select(Xutm, Yutm)
# 
# FutResFoots <- st_multipoint(x = as.matrix(FutResAllPoints)) # all the future/reserve trees foot
# FutResAllPoints <- st_cast(st_sfc(FutResFoots), "POINT", group_or_split = TRUE) # multiple points

# Distances between each of these points and Foot
RotationAngle <- c() # empty vector for rotation angles
for (FRP in 1:length(FutResAllPoints)) { # for each point
  FutResDist <- st_distance(Foot, FutResAllPoints[[FRP]]) # compute the distance for each point

  # If distances < TreeHeight of the tree to be felled
  if(FutResDist < dat$TreeHeight){
    # sum(FutResDists < dat$TreeHeight) # check av/res trees close to the tree to be felled

@@

        RotationAngle <- c(RotationAngle, as.numeric(matlib::angle(
          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - FootBuffer[[P]][2]), # position to avoid
          degree = TRUE)- 180))

@@

        RotationAngle <- c(RotationAngle, as.numeric(matlib::angle(
          c(FootBuffer[[P]][1] - FootBuffer[[P]][1], dat$TreeHeight), # default position
          c(FutResAllPoints[[FRP]][1] - FootBuffer[[P]][1], FutResAllPoints[[FRP]][2] - 
              FootBuffer[[P]][2]), # position to avoid
          degree = TRUE)))
      }
    }
  }else{AnglesToAvoid <- NULL}
}
rm(FutResDist)
# sum(!is.na(RotationAngle)) # check for how many av/res trees the angle has been computed

## Then the angle to the trail: the angle to avoid
OppAngToAvoid <- RotationAngle - theta

TrailAnglesToAvoid <- 180-(90 + OppAngToAvoid)
TrailAnglesToAvoid <- round(TrailAnglesToAvoid, digits = 0)
TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] <- TrailAnglesToAvoid[TrailAnglesToAvoid >= 360] - 360

AnglesToAvoid <- TrailAnglesToAvoid[
 TrailAnglesToAvoid >= 1 & TrailAnglesToAvoid <= 179
]
```

@@

```{r}
# Drop the tree between [1; 179°] avoiding the angles of the futures/reserves
if(dat$TreeFellingOrientationSuccess == "1"){

@@

    Aangle <- round(as.numeric(180 + OppAng + theta), digits = 0) # Foot oriented

@@

    Aangle <- round(as.numeric(360 - OppAng + theta), digits = 0) # Foot oriented
  }

@@

}else{ # else random felling
  RandomAngle <- as.numeric(sample(c(0:359), size = 1))
